Simulation for Correlation Motif

### 2017-09-16 analysis/Simulation.Rmd
wflow_publish("Simulation.Rmd")

The framework of Correlation Motif model is based on my [write-up document](../paper/Cormotif.pdf) and supplementary matrials by [$Wei$ $and$ $Ji$ (2015)][wj]. In $Wei$ $and$ $Ji$ (2015), they implemented an EM algorithm and introduced priors for both $\pi$ and $Q$. As a result, their iterative formulas for new $\pi$ and new $Q$ are:

@@

[wj]: https://doi.org/10.1093/biostatistics/kxu038

>>>>

The framework of Correlation Motif model is based on my [write-up document][wud] and supplementary matrials by [$Wei$ $and$ $Ji$ (2015)][wj]. In $Wei$ $and$ $Ji$ (2015), they implemented an EM algorithm and introduced priors for both $\pi$ and $Q$. As a result, their iterative formulas for new $\pi$ and new $Q$ are:

@@

[wud]: https://github.com/stephenslab/cormotif/blob/master/paper/Cormotif.pdf
[wj]: https://doi.org/10.1093/biostatistics/kxu038
